Improving Usability of Remote Access to Sensitive Data

### 2014-07-24 ccsw14/paper.tex
added to discussion section

@@

@@

%secure client access w/TPM
% -secure client
% -secure VNC connection

@@

%automating part/all of result release audit
%\label{sec:Results Audit}

@@

In eu gravida ligula, sit amet tincidunt nisi. Interdum et malesuada fames ac
ante ipsum primis in faucibus.  Vestibulum venenatis non sem vitae hendrerit.
Cras accumsan vel mauris ut vestibulum. Pellentesque auctor quam ut nisl
commodo malesuada. Phasellus adipiscing placerat tortor, in convallis massa
cursus eu. Vestibulum ullamcorper lorem vel nunc dictum, elementum pretium
nulla tincidunt.

>>>>

\textbf{Legitimate Release Channels} When researchers have finished working with
sensitive data, they must be given some channel for releasing their final
results.  Since this channel is purpose-built for releasing data that is a
reflection of the data being protected, safeguards must be put in place to
ensure that ``too much" information is not leaked.

@@

Although a basic prototype has been implemented and is fully functional, there
are still many potential routes for improvement.  We discuss many of these,
including some we are currently investigating and some that we intend to look
into in the future.

\subsection{Securing Client Access}

As mentioned in Section \ref{sec:Threat Model}, the channels used to access a VM
are an important element that must be secured in order to safeguard any private
data.  In the event of more sophisticated attacks, such as a man-in-the-middle
attack between the end user and the Data Capsules infrastructure or a compromise
of the end user's device, it is not hard to conceive of very powerful attacks.

For instance, if an end user's device is compromised, the malicious party could
then install malicious software on the VM while in maintenance mode that is
designed to enter secure mode and subsequently encode all of the private data in
the format of the channel medium (e.g. as an image in the case of remode desktop
protocols like VNC).  The data could then be decoded by additional software
running on the compromised client, or even forwarded for decoding on the
attacker's personal infrastructure.  In the case of a 1024x768 screen resolution
refreshing at 15 times per second, an attacker could leak over 2 GB of data from
a protected repository within one minute, or at the very least saturate the
channel connection with the leaked data.

This example clearly illustrates the imperative need to secure the remote access
channel from these types of attack.  There is also, however, a limit to what can
be done, since the user ultimately must have some way of seeing into the VM that
they are remotely administering.  The first obvious step is to secure the
client-server connection using SSL with certificate-based authentication.  While
this would seem trivial to accomplish, there is an unfortunate lack of support
for such a secure connection in existing widely used VNC clients.  We are
currently in the process of modifying an existing VNC client to support SSL
connections with certificates.  Beyond this initial setback, we expect
implementation to be relatively trivial.

Beyond securing the connection, we are currently investigating methods for
securing the end client device using the Trusted Platform Module (TPM) on an end
user's device to remotely attest that the end client is secure.  We envision the
final implementation will consist of a USB thumb drive containing a barebones
Linux operating system with an installed VNC client, and will use the TPM's
features to perform a measured boot of Linux and the VNC client.  Users will
plug in the USB drive to their device and boot into the secure environment in
order to access their Data Capsules VMs.  In this way, we hope to greatly raise
the bar for a malicious attacker who wishes to gain access to sensitive data,
while preserving a reasonably uncumbersome method for access to the end user.

\subsection{Optimizing Mode Switches}

@@

@@

\subsection{Partial Automation of Release Auditing}
\label{sec:Results Audit}

%automating part/all of result release audit

\subsection{Evaluation}

\subsubsection{User Study}

\subsubsection{Performance}

@@
